---
output:
  pdf_document: default
  html_document: default
---
Lab 2 
Andrew Maybach

Package used
```{r Packages}
library(igraph)
```
Reading in the file
```{r I/O}
dat = read.csv("C:/Users/amayb/Desktop/School/Fall 2018/IDS 564- Social Media & Network Analysis/Lab2/MergerNet_Jan21_2016_forR.csv")

```
Setting up the graph
```{r Graph}
graph = graph.data.frame(dat, directed = TRUE, vertices= NULL)
# List of all the years represented in the set
#dat[,"year"]
df <-data.frame(dat)

```
Stats and answers to problem 1.
```{r Desc and Problem 1}
#brief explanation of dataframe
str(df)
#edges
ecount(graph)
# Vertices
vcount(graph)

```
First Plot
```{r Original Plot}

plot(graph)
```
Is the graph a simple graph?

```{r Simple?}

is.simple(graph)

```
Making a simple graph and inspection for problem 2
```{r Simplified graph and simplified with weight}
graph_simpl<-simplify(graph)

#E(graph_simpl)$weight 
# Will use the inverse of log weight for shortest path calculations

inv_weight<-1/log(E(graph)$weight  + 1)
num_weight<-E(graph)$weight 

head(inv_weight)
#length(inv_weight)

plot(graph_simpl)
```
Sub graph
```{r Sub- Network}
sub_net = induced.subgraph(graph_simpl, v=c('511', '541',
'518', '519', '517', '325', '423', '446', '512', '523',
'561', '621', '115', '482', '485', '487', '491', '492',
'521', '712' ))


special_nodes = c('511','541','518','519')
```
Problem 3


```{r Problem 3}
graph_simpl_2= graph_simpl
graph_simpl_2$weight = inv_weight
diameter(graph_simpl_2)

```
Problem 4

```{r Problem 4}
inv_weight2<-1/log(E(graph_simpl)$weight  + 1)
num_weight2<-E(graph_simpl)$weight 


btw = betweenness(graph_simpl,directed = TRUE,weights = inv_weight2,normalized = TRUE,nobigint = TRUE)
#btw[special_nodes]

```
Problem 5

```{r Problem 5}
closeness(graph_simpl,V(graph_simpl)[special_nodes],mode= c('out'), weights = num_weight2, normalized=FALSE)

```
Problem 6
```{r Problem 6}
closeness(graph_simpl,V(graph_simpl)[special_nodes],mode= c('in'), weights = num_weight2, normalized=FALSE)

```
Problem 7
```{r Problem 7}
transitivity(graph)
#transitivity(graph, type= 'average') 
#mean(transitivity(graph, type= 'local'))
#fixed per the quiz update
```
Problem 8
```{r Problem 8}
dists = shortest.paths(graph_simpl, V(graph_simpl),V(graph_simpl),
  weights = inv_weight2)
dists[special_nodes,'814']
```
Problem 9
```{r Problem 9}
dists2 = shortest.paths(graph_simpl, V(graph_simpl),V(graph_simpl),
  weights = inv_weight2)
dists2['711',special_nodes]
#do not like the answers given here when compared to the quiz options
```

Problem 10
```{r Problem 10}
sub_net2 = induced.subgraph(graph_simpl_2, v=c('511', '541',
'518', '519', '517', '325', '423', '446', '512', '523',
'561', '621', '115', '482', '485', '487', '491', '492',
'521', '712' ))
diameter(sub_net2)
#do not like the answer that is given here when compared to the answers possible in the quiz
```
 Below are the parameters used to generate the sub network with varying specifications per the assignment

```{r Plotting Parms}
log_weights = log(E(sub_net)$weight) 
layout = layout_with_fr(sub_net)
node_size = sqrt(degree(sub_net))

V(sub_net)$color ='yellow'
V(sub_net)[special_nodes]$color = 'red'
```


```{r Plot}
png('plot.png',width = 1200,height = 1200)

plot(sub_net,main= "Special Nodes" ,
     layout=layout,
     vertex.size = node_size,
     edge.width = log_weights)
```






